\definemonster{bear}{Bears}
{
    Large heaps of muscle and fur. Any wounds ordinary weapons can inflict are likely only to make them more irate still.
}
{
    4-6 STR, 0-1 REF, 0-1 Claw'n'Maw (proficiency)
}

\definemonster{warg}{Wargs}
{
    The larger, stronger, nastier cousins of wolves. It is said they delight in evil and cruelty, though scholars
    are dubious on this point. It is generally agreed, however, that wargs tend to lead packs of their lesser kin
    instead of banding together themselves.
}{
    1-2 STR, 0-2 REF, 1-2 Claw'n'Maw (proficiency)
}

\definemonster{wolf}{Wolves}
{
    Slender, but strong, and silent until they attack. A single wolf should not pose a great threat to a determined
    man\footnote{Or a woman, for that matter} with a sword, but they tend to come in packs.
}{
    0-1 STR, 0-2 REF, 0-1 Claw'n'Maw (proficiency)
}

\definemonster{harpy}{Harpies}
{
    Roughly Halfling-sized, feathered creatures, chiefly found in areas with rough cliffs.
}{
    (-1)-0 STR, 1-2 REF, 0-1 Claw'n'Maw (proficiency)
}

\linkability{harpy}{fly:humanoid}

\definemonster{rotfiend}{Rotfiends}
{
    Of humaniod shape, but with pale, sickly yellow-ish skin and thick, protruding, deeply red veins. Like
    with most necrophages, their stench proceeds them. When terminally wounded, they are prone to explode
    spectacularily. This is their true danger, since their blood is poisonous.
}{
    0-1 STR, 0-1 REF, 0-1 Strangle (proficiency)
}

\linkability{rotfiend}{selfdetonation:rotfiend}

\definemonster{noonwraith}{Noonwraiths}
{
    Usually the restless souls of those who came to a violent end in the fields by day. They scorch the earth around them
    and can become quite dazzlingly bright. Since they are scolding hot, every turn in close combat results in a minor injury.
}{
    1-2 REF, 0-1 STR, 1-2 Wraith's wrath (proficiency, used in ability-rolls)
}

\linkability{noonwraith}{blinding}
\linkability{noonwraith}{restoration:spectre}

\definemonster{nightwraith}{Nightwraiths}
{
    Usually the restless souls of those who came to a violent end in the fields by night. They freeze the grass around them
    and can emit fearsomely frosty fog. Since they are deadly cold, every turn in close combat results in a minor injury.
}{
    1-2 REF, 0-1 STR, 1-2 Wraith's wrath (proficiency, used in ability-rolls)
}

\linkability{nightwraith}{freezingfog}
\linkability{nightwraith}{restoration:spectre}

% Not yet included in the main file to avoid merge conflicts

\definemonster{drowner}{Drowners}   % Necrophage
{
    The largely humanoid shape, bloated abdomen and pale blue-ish to green-ish colour give rise to the common
    misconception that drowners are the reanimated corpses of unlucky travellers who found their untimely end 
    in some body of water. Witchers and academics with strong bowels and a strange taste, however, have seen 
    the scales on their skin, the fins on their back and the gills between their fingers and so concluded that
    these unhappy creatures are simply a race of scavengers brought into the world by the conjunction of spheres.

    Drowners can be found where there are water and rot in close proximity, and occasionally, during heavy rains, 
    even further inland. They are cravens, though it is not unheard of that they would attack lone travellers, 
    especially if these are injured. The only way in which they pose a real threat to a careful human is by catching
    them in the water: Here, their name is fully justified as they will seek to pull under anything they find 
    struggling on the surface, to drown it and eat it once dead. 

    Drowners have cousins, but the Muire D'yaeblen of \nameref{region:skellige} are not one of them: They are 
    genetically identical to the drowners of the continent, though often a little tougher \textendash like the
    \hyperref[people:skellige]{humans of the isles}.
    \\[1.5ex]
    Drowners receive no detriment from being submerged in water and are higly resistant to poisons. Since the karp
    they share their natural habitat with are also their intellectual peers, magic affecting the mind does not work
    on them.
}{
    0-1 REF, -1 INT, 0-1 Strangle (proficiency)
}

\definemonster{drowned_dead}{Drowned Dead}
{
    These monsters are akin to \hyperref[monster:drowner]{drowners} and, to the layperson, unintelligible from them. Even
    professionals will have a hard time to tell the two apart at a distance, though from close up, there are signs,
    if you know where to look \textendash their eyes give it away, for one thing. The appearance of drowned dead is 
    often linked to the nearby death of particularily vicous criminals, but whether it is in fact the deceased 
    walking\footnote{Or swimming} once more or merely a remnant of their malice imbued in the body of a scavenger
    is a point of contention. It is widely accepted that the darkest legends of \hyperref[monster:drowner]{drowners}
    actually feature this subspecies rather than their cowardly cousins.
    \\[1.5ex]
    Like all \hyperref[monster:drowner]{drowners}, the drowned dead are immune to manipulation of their minds and
    unhindered by submersion in water or poison.
}{
    0-1 REF, -1 INT, 1-2 Strangle (proficiency)
}

\definemonster{mucknixer}{Mucknixers}
{
    A more dangerous subspecies of \hyperref[monster:drowner]{drowner}, distinguishable by their darker hue and 
    more pronounced dorsal fins. They can be found in the bogs of \nameref{region:velen} and by the coasts of
    \hyperref[region:skellige]{Skellige}.
    \\[1.5ex]
    Like all \hyperref[monster:drowner]{drowners}, mucknixers are immune to manipulation of their minds and
    unhindered by submersion in water or poison.
}{
    0-1 STR, 0-1 REF, -1 INT, 0-1 Strangle (proficiency)
}