% Realms

\definerealm{aedirn}{Aedirn}
{
    Situated between \hyperref[region:mahakamMtns]{the mountains of Mahakam} to the west, \nameref{realm:kaedwen} to the north and
    \hyperref[region:blueMtns]{the Blue Mountains} to the east, \nameref{realm:aedirn} is shielded from harsh weather by the surrounding mountain
    ranges. This kind and consistant climate, along with \hyperref[region:pontar]{the Pontar Valley}, have enabled a strong agricultural economy
    to flourish. Further, the proximity to Mount Carbon has lead to the development of considerable industry in the western parts of the kingdom.
    \nameref{realm:aedirn} is ruled by king Demavend the Third.
}

\definerealm{cintra}{Cintra}
{

}
{}

\definerealm{kaedwen}{Kaedwen}
{
    The largest of the Northern Realms, \nameref{realm:kaedwen} shares borders with both \nameref{realm:redania} and \nameref{realm:aedirn}.
    The kingdom's ruler is king Henselt, who has continued the petty wars and skirmishes with \nameref{realm:aedirn} that have been occurring
    for many decades over which realm gets to control the \hyperref[region:pontar]{Pontar Valley}. To date, the region is held by \nameref{realm:aedirn}.
}

\definerealm{nilfgaard}{Nilfgaard}
{
    The North is faced by one singular Enemy: The Nilfgaardian Empire that subjugated or conquered all 
    provinces south of the Yaruga. It's recent line of emperors was broken by the Usurper, who had
    Fergus var Emreis assassinated and seized the throne for himself. He was in turn overthrown by the previous
    emperor's heir, Emhyr var Emreis. Emhyr undid the Usurper's reforms and began reaching northwards, but was 
    defeated twice, claiming only \nameref{realm:cintra} after his second failed invasion. The empire's strong 
    economy led to a victory of sorts, however: The devastated North was forced to rely on grain and goods imported
    from their southern foe, weakening their own economies.
    
    \paragraph{Vassal states}
    \begin{itemize}
        \item \nameref{realm:cintra}
        \item \nameref{realm:toussaint}
    \end{itemize}
}

\definerealm{redania}{Redania}
{
    Ruled at the moment by king Radovid the Stern, the kingdom profits greatly from trade with the other realms of the north.
    The chief source of \nameref{realm:redania} are her export of grain to less fertile regions, though recently cheaper
    imports from \nameref{realm:nilfgaard} have begun threatening this key factor of the Redanian economy.
    \nameref{realm:redania} stands in a long tradition of war with \nameref{realm:temeria}, however, the two kingdoms have
    grown closer during the reign of Radovid.
}

\definerealm{temeria}{Temeria}
{
    \nameref{realm:temeria} lies south of the \hyperref[region:pontar]{Pontar} and west of \nameref{realm:aedirn}. To her west lie the smaller realms of 
    Cidaris and Verden, as well as the ancient forest of \nameref{region:brokilon}. The \hyperref[realm:temeria]{Temerian} army defeated the recent 
    \hyperref[realm:nilfgaard]{Nilfgaardian} invasion and King Foltest used this success and the chaos left behind by the war
    to expand his influence over the \hyperref[region:mahakamMtns]{mountains of Mahakam} and the southern regions of Sodden and Brugge.
}

\definerealm{toussaint}{Toussaint}
{
    Toussaint appears as an idyllic region right out of a wondertale: Mild climes, blue waters and volcanic rock make 
    the duchy the source of the continent's finest wines. It is a vassal of \nameref{realm:nilfgaard}, but largely 
    autonomous and gouverned in most matters by the duchess Anna Henrietta. Traditions of chivalric virtue are held in 
    high esteem by the Toussaintese, and the executive arm of gouvernement consists almost entirely of \hyperref[profession:knight_errant]{Knights-errant},
    bound by honour rather than pay. The duchy was also the location in which, during the conjecture of spheres, the 
    gate to the world of vampires opened.
}

% Cities
\definecity{vengerberg}{Vengerberg}
{
    The capital city of \nameref{realm:aedirn} and in days gone by one of the richest and most populous cities in the north. In the most recent war
    with \nameref{realm:nilfgaard}, however, it was sacked, and has since only slowly begun rebuilding.
}
{aedirn}

\definecity{ard_carraigh}{Ard Carraigh} 
{ 
    The capital city of \nameref{realm:kaedwen}, though lesser in most ways than \nameref{city:ban_ard}.
}
{kaedwen}

\definecity{ban_ard}{Ban Ard}
{
    Likely the most important city in \nameref{realm:kaedwen} and home to the powerful sorcerers' academy.
}
{kaedwen}

\definecity{nilfgaard}{The city of Nilfgaard}
{
    The `City of Golden Towers' is the heart and cradle of the empire. It lies on the river Alba and is connected to the
    sea by a nearby harbour.
}
{nilfgaard}

\definecity{novigrad}{The Free City of Novigrad}
{
    Although geographically part of \nameref{realm:redania}, the city of \hyperref[city:novigrad]{Novigrad} is not ruled by Radovid but rather self-gouverned.
    She has by trade become the richest city of the north, a success due largely to her haven - one of the greatest on the entire continent.

    The Church of the Eternal Fire has an influence greater than anywhere else in the \hyperref[city:novigrad]{Free City}, its greatest temple towers over the city atop a sheer cliff.
    Hence it is an unfortunate truth that nowhere else can such animosity towards non-humans be found, and witch-hunts are a gruesome factor of life in \hyperref[city:novigrad]{Novigrad}.

    Officially, the Free City is gouverned by a city council, but in fact all real power rests in the hands of four criminal organizations:
    \begin{itemize}
    	\item Whoreson Junior's gang, involved in gambling and brothels and the like. They are, as a rule, despised even by their peers.
    	\item Sigi Reuven's gang, lead by the former redanian agent Sigismund Dijkstra, mostly lurks in the shadows of the town.
    	      How exactly they make ends meet is unknown, however the assumption that it is connected to clandestine activities of some sort
    	      is quite obious.
    	\item The inhabitants of the secret street aptly named ``the Putrid Grove'' led by Francis Bedlam, the ``King of Beggars''.
    	      The group consists mostly of thieves and beggars who find refuge and pawn shops in their home street.
    	\item Cleaver's gang mostly consists of dwarves, quite sensibly, as Cleaver himself is a dwarf. It specializes on thuggery of all
    	      kinds and practically amounts to a small army.
    \end{itemize}
}
{redania}

\definecity{oxenfurt}{Oxenfurt}
{
    A small town by comparison, with its centre situated on an island in the \hyperref[region:pontar]{Pontar}. It is well renowned for it's academy
    which supports the natural sciences and almost entirely fills the cities centre, either directly with its large campus, or indirectly
    with pubs and similar establishments frequented by students and teachers alike. The town was built upon the ruins of an elven settlement,
    however, the ancient brickwork can nowadays only be admired by anyone unfortunate enough to find their way into the sewers.
}
{redania}

\definecity{tretogor}{Tretogor}
{
    The capital city of \nameref{realm:redania}, known mostly for the annual horse race, the ``Grand Tretorian,'' held here.
}
{redania}

\definecity{gors_velen}{Gors Velen}
{
    The city lies in a natural bay by the ocean, a little south of the \hyperref[region:pontar]{Pontar}. Thanks to it's location,
    Gors Velen is an importand northern trade centre, second only to \nameref{city:novigrad}. Considering the spot is a good one
    to put a city, it is hardly surprising that Gors Velen, too, is built upon the ruins of an older Elven city.
}
{temeria}

\definecity{vizima}{Vizima}
{
    The capital city of \nameref{realm:temeria} lies beside the beautiful Lake Vizima. It is the meeting-point of many
    important trade routes and holds within it's walls the Royal Palace of the \hyperref[realm:temeria]{Temerian} Dynasty.
}
{temeria}

\definecity{beauclair}{Beauclair}
{
\dots
}
{toussaint}